The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-07-26 paper/ms.tex
all stars now listed

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

@@

We selected as our sample all stars on-silicon in \kepler with $Kp<8$ which were unobserved for more than $10$ quarters \textcolor{red}{Tim: what was your cutoff in quarters for `underobserved' stars?}, including those stars which were entirely unobserved. A number of these lay just at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded. After applying these criteria we obtained a list of \textcolor{red}{101} targets. Aside from the restriction on stars falling on the edge of a chip, the addition of these objects to conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=8$.

@@

>>>>

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{longtable}

@@

We selected as our sample all stars on-silicon in \kepler with $Kp<8$ which were unobserved for more than $10$ quarters \textcolor{red}{Tim: what was your cutoff in quarters for `underobserved' stars?}, including those stars which were entirely unobserved. A number of these lay just at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded. After applying these criteria we obtained a list of \textcolor{red}{101} targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, the quarters for which they were observed, the seasons for which they were on silicon (some did not even land on silicon for all seasons) and whether spectroscopy is available as in Section~\ref{spectroscopy} and Table~\ref{stellar_props}. Aside from the restriction on stars falling on the edge of a chip, the addition of these objects to conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=8$.

@@

\input{all_stars.tex}
\input{all_Stars2.tex}
